\LARGE \bf Lightweight Vision Based Multiple Target Tracking Using Deep Learning and Recursive RANSAC

### 2017-12-20 project/paper/paper.tex
Finished paper

Currently, military UAV's are usually equipped with expensive gimballed cameras that are able to view targets such as people or vehicles from a high altitude. Those targets are being tracked by pilots who are remotely controlling the aircraft. This task can be difficult and time consuming for humans to track a target over the course of several hours. In order to improve the capabilities of UAV's to track ground targets autonomously, a neural network is proposed to learn targets and track them even after loosing visual line of sight temporarily.

In this report, we will discuss the current capabilities of UAV's and where there exist technology gaps in their abilities to perform well in ISR missions. In section \ref{BACKGROUND}, we present the history and current work that has been done already to autonomously track ground targets from a ISR UAV. In this section, we will also discuss the importance of why a neural network could be useful in this application. Following this, in section \ref{METHODS}, our attempted methods to improve the existing capabilities with neural networks will be presented. The reader will then be able to read the results in \ref{RESULTS} and our final conclusion in \ref{CONCLUSION}.

@@

This project is not designed to create an end-to-end target tracking system using neural networks. That has already been done by several others already and it currently too computationally expensive to run on a small embedded computer. \textbf{The goal of this project is to integrate a neural network into the Visual Multi-Target Tracker (Visual MTT) that uses Recursive RANSAC to track targets. The roll of the neural network is to classify and identify the target when Visual MTT creates a new track.} With every new track Visual MTT creates, it will query the neural network and see if it has seen that target before. If it has, it Visual MTT will then associate this new target track with the old target track. The roll of a neural network in this system is illustrated in Figure \ref{fig:rransac}.

Although the primary purpose of this project was to design a neural network around classifying target images, most of the time spent went towards collecting a good dataset to train and test on. Unfortunately, all of the data collected from actual flight tests and imagery at Brigham Young University wasn't able to be used because of the low quality of the images. Further details of this are discussed below.

@@

\begin{figure*}
	\begin{center}
		\includegraphics[width=.85\textwidth]{rransac.png}
		\caption{\textit{This block diagram shows how a neural network plays a roll in the Visual MTT framework. The scope of the work for this project is shown in green.}} 
		\label{fig:rransac}
	\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{BACKGROUND AND MOTIVATION} \label{BACKGROUND}

@@

The second factor in why targets are lost is because of human error. The military currently uses pilots/co-pilots to visually track the target on the ground using a video feed they receive back at their ground station. This video feed is subject to temporary glitches in the streaming service that can cause interruption of the video. Upon regaining the video feed, the gimballed camera may need to be realigned with the target. Given the image as observed in Figure \ref{fig:gimbal_far}, this may be difficult for a human operator to do if the scene is in a cluttered, pattern-like environment such as a city. The operator may not be able to visually recognize the desired target anymore. Human operators are also subject to boredom and fatigue when tracking a ground target for many hours.

@@

R-RANSAC, however, is subject to some limitations. One of the primary limitations of R-RANSAC is that when a target is temporarily unobserved, ie. the target goes off the frame of the camera or the target moves behind an occlusion, the target is lost. The other main limitation with R-RANSAC is its inability to track static targets. If a target were to stop momentarily and then continue on, R-RANSAC would initialize a new track and make no correlation between the new track and the old one. It is the same case for when a target is temporarily blocked from the field of view.

@@

To simplify things, only two targets were present during the collection of the video data. This was intentionally the case to make the training and testing of the neural network much faster and simpler. We used the Anaconda UAV from ReadyMade RC products. This aircraft is capable of flying for an hour while carrying on-board a gimballed camera and an embedded computer. This aircraft can be seen in Figure \ref{fig:anaconda}. The camera we used was a low-cost global shutter camera called the PointGray Chameleon. It was on a two-axis gimbal mechanism that allowed the camera to pan and tilt. This camera setup can be seen in Figure \ref{fig:gimbal}. The images shown in \ref{fig:gimbal_far} and \ref{fig:gimbal_zoomed} are from this UAV and camera setup. The video was recorded on-board so we could test our neural network through several iterations.

\begin{figure}
	\begin{center}
		\includegraphics[width=.45\textwidth]{gimbal.jpg}
		\caption{\textit{This PointGrey Chameleon camera attached to a gimbal is what was used to collect the video data.}} 
		\label{fig:gimbal}
	\end{center}
\end{figure}

@@

The network that was ultimately used was the VGG-16 network through convolution 5-3. Then four fully connected layers were constructed with output sizes of 256, 128, 64, and 7, in that order. An illustration of this network can be seen in Figure \ref{fig:cnn}. This was a fairly traditional CNN. The primary way this CNN was unique was in the way data was passed to the CNN. With only one frame coming in at a time from a live video feed, this means that the network can only train on a few images at a time. When multiple targets were in the camera image, the network would be able to train on more than just one target. This caused several issues with feeding the network because the batch size was now a variable size. For this reason, I was unable to get the network to train.

@@

Although the end result of the neural network is currently disappointing, I learned a lot in the process.

>>>>

Currently, military UAV's are usually equipped with expensive gimbaled cameras that are able to view targets such as people or vehicles from a high altitude. Those targets are being tracked by pilots who are remotely controlling the aircraft. This task can be difficult and time consuming for humans to track a target over the course of several hours. In order to improve the capabilities of UAV's to track ground targets autonomously, a neural network is proposed to learn targets and track them even after loosing visual line of sight temporarily.

In this report, we will discuss the current capabilities of UAV's and where there exist technology gaps in their abilities to perform well in ISR missions. In section \ref{BACKGROUND}, we present the history and current work that has been done already to autonomously track ground targets from a ISR UAV. In this section, we will also discuss the importance of why a neural network could be useful in this application. Following section \ref{BACKGROUND}, in section \ref{METHODS}, our attempted methods to improve the existing capabilities with neural networks will be presented. The reader will then be able to read the results in \ref{RESULTS} and our final conclusion in \ref{CONCLUSION}.

@@

This project is not designed to create an end-to-end target tracking system using neural networks. That has already been done by several others already and it currently too computationally expensive to run on a small embedded computer. \textbf{The goal of this project is to integrate a neural network into the Visual Multi-Target Tracker (Visual MTT) that uses Recursive RANSAC to track targets. The role of the neural network is to classify and identify the target when Visual MTT creates a new track.} With every new track Visual MTT creates, it will query the neural network and see if it has seen that target before. If it has, Visual MTT will then associate this new target track with the old target track. The roll of a neural network in this system is illustrated in Figure \ref{fig:rransac}.

Although the primary purpose of this project was to design a neural network around classifying target images, most of the time spent went towards collecting a good dataset to train and test on. Unfortunately, all of the data collected from actual flight tests and imagery at Brigham Young University was not able to be used because of the low quality of the images. Further details of this are discussed below.

@@

\begin{figure*}
	\begin{center}
		\includegraphics[width=.85\textwidth]{rransac.png}
		\caption{\textit{This block diagram shows how a neural network plays a roll in the Visual MTT framework. The scope of the work for this project is shown in green.}} 
		\label{fig:rransac}
	\end{center}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{BACKGROUND AND MOTIVATION} \label{BACKGROUND}

@@

The second factor in why targets are lost is because of human error. The military currently uses pilots/co-pilots to visually track the target on the ground using a video feed they receive back at their ground station. This video feed is subject to temporary glitches in the streaming service that can cause interruption of the video. Upon regaining the video feed, the gimbaled camera may need to be realigned with the target. Given the image as observed in Figure \ref{fig:gimbal_far}, this may be difficult for a human operator to do if the scene is in a cluttered, pattern-like environment such as a city. The operator may not be able to visually recognize the desired target anymore. Human operators are also subject to boredom and fatigue when tracking a ground target for many hours.

@@

R-RANSAC, however, is subject to some limitations. One of the primary limitations of R-RANSAC is that when a target is temporarily unobserved, i.e. the target goes off the frame of the camera or the target moves behind an occlusion, the target is lost. The other main limitation with R-RANSAC is its inability to track static targets. If a target were to stop momentarily and then continue on, R-RANSAC would initialize a new track and make no correlation between the new track and the old one. It is the same case for when a target is temporarily blocked from the field of view.

@@

To simplify things, only two targets were present during the collection of the video data. This was intentionally the case to make the training and testing of the neural network much faster and simpler. We used the Anaconda UAV from Ready Made RC products. This aircraft is capable of flying for an hour while carrying on-board a gimbaled camera and an embedded computer. This aircraft can be seen in Figure \ref{fig:anaconda}. The camera we used was a low-cost global shutter camera called the Point Gray Chameleon. It was on a two-axis gimbal mechanism that allowed the camera to pan and tilt. This camera setup can be seen in Figure \ref{fig:gimbal}. The images shown in \ref{fig:gimbal_far} and \ref{fig:gimbal_zoomed} are from this UAV and camera setup. The video was recorded on-board so we could test our neural network through several iterations.

\begin{figure}
	\begin{center}
		\includegraphics[width=.45\textwidth]{gimbal.jpg}
		\caption{\textit{This Point Grey Chameleon camera attached to a gimbal is what was used to collect the video data.}} 
		\label{fig:gimbal}
	\end{center}
\end{figure}

@@

The network that was ultimately used was the VGG-16 network through convolution 5-3. Then four fully connected layers were constructed with output sizes of 256, 128, 64, and 7, in that order. An illustration of this network can be seen in Figure \ref{fig:cnn}. This was a fairly traditional CNN. The primary way this CNN was unique was in the way data was passed to the CNN. With only one frame coming in at a time from a live video feed, this means that the network can only train on a few images at a time. When multiple targets were in the camera image, the network would be able to train on more than just one target. This caused several issues with feeding the network because the batch size was now a variable size. For this reason, I was unable to get the network to train. The loss function was the sparse softmax cross entropy between the label and the fourth fully connected layer.

@@

Although the end result of the neural network is currently disappointing, I learned a lot in the process. One of the core concepts I learned was to start with the most simplified data you can possibly start with. Several hours would have been save had I found the Atrium dataset at the beginning of the project. I also learned a lot about the current capabilities of neural networks in detecting and classifying objects. This has been valuable research for my thesis work as I am attempting to track multiple targets from a small UAV. The research done for this project will be continued on over the next several weeks to possibly make a more robust target tracker.
